---
title: "p8105_hw1_jsg2145"
author: "Jared Garfinkel"
date: "9/17/2019"
output: github_document
---

# Data Science I P8104

I am in Data Science I P8104.

## HW1

This is my first homework assignment.

### Problem 1

This is the first problem of the problem set. Load the library.

```{r load library}
library(tidyverse)
```

Here's a dataframe.

```{r create a dataframe}
df1 = tibble(
  samp = rnorm(8),
  samp_pos = samp > 0,
  char_vec = c("This", "is", "a", "character", "vector", "of", "length", "eight"),
  fact_vec = factor(c("fac1", "fac2", "fac3", "fac4", "fac5", "fac6", "fac7", "fac8")))
```

Take the mean of each vector:

I can take the mean of samp = `r mean(pull(df1, samp))`

I can take the mean of samp_pos = `r mean(pull(df1, samp_pos))`, but it won't tell me much

The mean of a character vector doesn't make sense, `r mean(pull(df1, char_vec))`

Neither does one for a factor, `r mean(pull(df1, fact_vec))`

```{r as.numeric, eval = FALSE}
pull(df1, samp_pos) %>% 
  as.numeric()

pull(df1, char_vec) %>% 
  as.numeric()

pull(df1, fact_vec) %>% 
  as.numeric()
```
My logical vector was converted to zeros and ones, 

whereas my character vector was converted to NAs "by coercion".

My factors were assigned number values from 1 to 8.

```{r conversions}
## This returns a zero, not sure why

df1n <- df1 %>% 
  mutate(
    samp_pos = as.numeric(samp_pos))
prod(
  pull(df1n, samp_pos),
  pull(df1n, samp))
```

```{r conversions 2, eval = FALSE}
## This next one doesn't work because a factor can't be multiplied

df1f <- df1 %>%
  mutate(
    samp_pos = as.factor(samp_pos))
prod(
  pull(df1f, samp_pos),
  pull(df1f, samp))
```

```{r conversions 3}
## The last one returns something more like what I expected, a random number

df1fn <- df1 %>% 
  mutate(
    samp_pos = as.factor(samp_pos)) %>% 
  mutate(
    samp_pos = as.numeric(samp_pos))
prod(
  pull(df1fn, samp_pos), 
  pull(df1fn, samp))
```

# Problem 2

Create a second dataframe.

```{r create a second dataframe}
set.seed(1)

df2 = tibble(
  x = rnorm(500),
  y = rnorm(500),
  gr_th1 = x + y > 1,
  gr_th1_num = as.numeric(gr_th1),
  gr_th1_fac = factor(gr_th1)
)
```

The size of this dataframe is `r nrow(df2)` rows by `r ncol(df2)` columns.

The mean of x is `r mean(pull(df2, x))`, the median of x is `r median(pull(df2, x))`, and

the standard deviation of x is `r sd(pull(df2, x))`. The proportion of cases for which x + y > 1

is `r sum(pull(df2, gr_th1))` / 500.

```{r Pipe, echo = FALSE, eval = FALSE}

## I tried to create a dataframe with a decent legend

df2_good <- df2 %>% 
  mutate(
    gr_th1_fac = factor(gr_th1_fac,
                        labels = c("No", "Yes"))) %>% 
  labs(fill = "Sum is greater than 1")
with(df2_good, 
     plot(x = pull(df2_good, x), y = pull(df2_good, y)))
```



```{r ggplot logical}
## This makes a plot using the logical vector to color points

ggplot(df2,
       aes(x, y, color = gr_th1)) +
  geom_point()
```

```{r ggplot factor}
## This makes a plot using the factor vector to color points

ggplot(df2,
       aes(x, y, color = gr_th1_fac)) +
  geom_point()
```


```{r ggplot numerical}
## This makes a plot using the numerical vector to color points

ggplot(df2,
       aes(x, y, color = gr_th1_num)) +
  geom_point()
```

The numerical and factor vectors came out as bicolor, and the numerical plot was a continuous scale. 
  

```{r this plot works, echo = FALSE, eval = FALSE}
with(df2, 
     plot(x, y))
with(
  filter(df2, gr_th1 == TRUE),
  points(x, y, col = 'red'))
with(
  filter(df2, gr_th1 == FALSE),
  points(x, y, col = 'blue'))
legend("bottomleft", pch= 1, col=c("blue","red"), legend=c("Sum not greater than 1","Sum greater than 1"))
```