---
title: "p8105_hw1_jsg2145"
author: "Jared Garfinkel"
date: "9/17/2019"
output: github_document
---

# Data Science I P8104

I am in Data Science I P8104.

## HW1

This is my first homework assignment.

### Problem 1

This is the first problem of the problem set. Load the library.

```{r load library}
library(tidyverse)
```

Here's a dataframe.

```{r create a dataframe}
df1 = tibble(
  samp = rnorm(8),
  samp_pos = samp > 0,
  char_vec = c("This", "is", "a", "column", "of", "length", "eight", "characters"),
  fact_vec = factor(samp, levels = list("factor1", "factor2", "factor3")))
```

Take the mean of each vector:

I can take the mean of samp = `r mean(pull(df1, samp))`

I can take the mean of samp_pos = `r mean(pull(df1, samp_pos))`, but it won't tell me much

The mean of a character vector doesn't make sense, `r mean(pull(df1, char_vec))`

Neither does one for a factor, `r mean(pull(df1, fact_vec))`

```{r as.numeric, eval = FALSE}
as.numeric(pull(df1, samp_pos))
as.numeric(pull(df1, char_vec))
as.numeric(pull(df1, fact_vec))
```
My logical vector was converted to zeros and ones, whereas my character vector was converted to NAs "by coercion".

My factors were unassigned, so they were also NA.

```{r conversions, eval = FALSE}
prod(as.numeric(pull(df1, samp_pos)), pull(df1, samp))
prod(as.factor(pull(df1, samp_pos)), pull(df1, samp))
prod(as.numeric(as.factor(pull(df1, samp_pos))), pull(df1, samp))
```

# Problem 2

Create a second dataframe.

```{r}
df2 = tibble(
  x = rnorm(500),
  y = rnorm(500),
  gr_th1 = x + y > 1,
  gr_th1_num = as.numeric(gr_th1),
  gr_th1_fac = factor(gr_th1)
)
```

The size of this dataframe is `r nrow(df2)` rows by `r ncol(df2)` columns.

The mean of x is `r mean(pull(df2, x))`, the median of x is `r median(pull(df2, x))`, and

the standard deviation of x is `r sd(pull(df2, x))`. The proportion of cases for which x + y > 1

is `r sum(pull(df2, gr_th1))/500`.

```{r}
ggplot(data = df2,
       aes(x = x, y = y, 
       color = ifelse(gr_th1 == TRUE, "blue", "red"),
       legend(legend = c("Sum not greater than 1", "Sum greater than 1")))) +
  geom_point()
  


with(df2, 
     plot(x, y))
with(
  filter(df2, gr_th1 == TRUE),
  points(x, y, col = 'red'))
with(
  filter(df2, gr_th1 == FALSE),
  points(x, y, col = 'blue'))
legend("bottomleft", pch=1, col=c("blue","red"), legend=c("Sum not greater than 1","Sum greater than 1"))
     
     
```