---
title: "p8105_hw1_jsg2145"
author: "Jared Garfinkel"
date: "9/17/2019"
output: github_document
---

# Data Science I P8104

I am in Data Science I P8104.

## HW1

This is my first homework assignment.

### Problem 1

This is the first problem of the problem set. Load the library.

```{r load library}
library(tidyverse)
```

Here's a dataframe.

```{r create a dataframe}
df1 = tibble(
  samp = rnorm(8),
  samp_pos = samp > 0,
  char_vec = list("1","2","3","4","5","6","7","8"),
  fact_vec = factor(levels = "factor1", "factor2","factor3"))
```

Take the mean of each vector:

I can take the mean of samp = `r mean(pull(df1, samp))`

I can take the mean of samp_pos = `r mean(pull(df1, samp_pos))`, but it won't tell me much

The mean of a character vector doesn't make sense, `r mean(pull(df1, char_vec))`

Neither does one for a factor, `r mean(pull(df1, fact_vec))`

```{r as.numeric, eval = FALSE}
as.numeric(pull(df1, samp_pos))
as.numeric(pull(df1, char_vec))
as.numeric(pull(df1, fact_vec))
```
I happened to use numbers for my character vector, so they were converted to numbers. 

However, my factors were characters and they did not convert to numbers.


